Composition-climate paper

### 2016-08-23 Composition_Ecology.Rmd
Edits for the Results, all the way through into the Discussion.

*The Discussion section should be separate from the Results section. It allows authors to propose their interpretation of the results, and to suggest what they might mean in a wider context. It should end with a clear statement of the main conclusions of the research, and a clear explanation of their importance and relevance.*

This work demonstrates that historic land use can substantially alter the realized climate niches of species and adds to our understanding of the interacting effects of climate change and land-use [@pyke2004habitat]. Land use change reduces the correlational structure between species and climate [@devineau2011arid] and is likely to have one of the strongest effects on changes in global biodiversity over the next century [@sala2000global]. While rates of land-use change may be declining in North America and in the upper Midwest [@dale1997landuse; @rhemtulla2009legacies] the legacies of land-use are likely to persist, both in terms of forest composition [@gorng2016preset;@kujawa2016theeffect], and the correlational structure between species and climate. This work reinforces the importance of historical datasets for examining the relationships between species and climate, and their importance in forecasting species distributions in the future [@moritz2013future;@maguire2015modeling]. Modern surveys sample only a subset of historical distribution, both spatially and within multidimensional climate space.

>>>>

This work reinforces the importance of historical datasets for examining the relationships between species and climate, and their importance for forecasting future species distributions [@moritz2013future;@maguire2015modeling]. Modern surveys sample only a subset of historical distributions, both spatially and within multidimensional climate space.  These analyses demonstrate that species-climate relationships have already begun to change, as a result of land use and climate chnage over the past few centuries, and adds to our understanding of the interacting effects of climate change and land-use [@pyke2004habitat]. Land use change reduces the correlational structure between species and climate [@devineau2011arid] and is likely to have one of the strongest effects on changes in global biodiversity over the next century [@sala2000global]. While rates of land-use change may be declining in North America and in the upper Midwest [@dale1997landuse; @rhemtulla2009legacies] the legacies of land-use are likely to persist, both in terms of forest composition [@gorng2016preset;@kujawa2016theeffect], and the correlational structure between species and climate.
